\section{Professional Experience}
\tabularBar{
\textsc{Present} & \textbf{Software Developer} at Spoud AG, Bern, Switzerland\\
\textsc{11/2017} & \small{Development of a real-time transport layer using Reactive Streams (RxJava), gRPC (with Protocol Buffers), Apache Kafka. Development of a REST API using Spring Web, JPA, Swagger.}\\
\multicolumn{2}{c}{}\\

\textsc{08/2017} & \textbf{Software Engineer} at Vodafone, Glasgow, Scotland\\
\textsc{04/2017} & \small{Development of a desktop application to automate neighbours planning in cellular networks. Improved the drop call rate of northern areas of the UK by more than 30\%.}\\
\multicolumn{2}{c}{}\\

\textsc{03/2017} & \textbf{Software Engineer R\&D} at Celfinet, Lisbon, Portugal\\
\textsc{10/2015} & \small{Research of geolocation algorithms for mobile and IoT networks using radio frequency propagation models. Improved the geolocation error of $\mathtt{\sim}$278 meter to less than 131 meter. Use of genetic algorithms to calibrate the models.}\\
\multicolumn{2}{c}{}\\

\textsc{09/2015} & \textbf{Software Engineer R\&D} at IT, Lisbon, Portugal\\
\textsc{01/2015} & \small{Software development of video processing algorithms: detection of black frames, black margins, flashes, block effect, removal of subtitles and inpaint.}
}

\section{Education}
\tabularBar{
\textsc{12/2014} & \textbf{MSc in Electrical and Computer Engineering}\\
\textsc{09/2007} & Instituto Superior T\'{e}cnico, Lisbon\\
& \small{Main Subjects: Algorithms and Data Structures, Computer Networks and the Internet, Information Systems and Databases, Mobile Communication Systems, Networks and Computer Security, Object Oriented Programming, Optical Fiber Telecommunication Systems, Radio Wave Propagation.}
}

\section{Publications}
\tabularNoBar{
\textsc{07/2015} & Roque, B., \quotationMarks{Improving Energy Efficiency in Cellular Networks Using Multicell Cooperation}, In: 10th Conference on Telecommunications, ConfTele 2015.\\
\textsc{05/2015} & Carreira, L. and Rodrigues, N. and Roque, B. and Queluz, M.P., \quotationMarks{Automatic Detection of Flashing Video Content}, In: Quality of Multimedia Experience (QoMEX) 2015.
}

\newpage

\section{Skills}
\begin{tabular}{r p{12cm}}
\textsc{Technologies:} & Java (Spring), Reactive Streams (RxJava), NodeJS (Typescript), Python, Golang, Apache Kafka, Docker\\
\textsc{Tools:} & IntelliJ, VSCode, Git, Bash/Zsh, Vim, Tmux\\
\textsc{Development:} & Test Driven Development, SOLID, Clean Code
\end{tabular}

\section{Professional Development}
\tabularNoBar{
\textsc{Present} & Genetic Algorithm, Blockchain, Decision Tree Player and other side projects on \gitHubNoUrl{}.\\
\textsc{02/2019} & \href{https://brunoroque06.github.io/documents/certificates/RestApiSpringUdemy.pdf}{Java Web Services and RESTful API with Spring}, by Udemy.\\
\textsc{01/2019} & \href{https://brunoroque06.github.io/documents/certificates/KafkaUdemy.pdf}{Learn Apache Kafka for Beginners v2}, by Udemy.\\
\textsc{11/2017} & \href{https://brunoroque06.github.io/documents/certificates/FrontEndUdacity.pdf}{Front-End Web Developer Nanodegree}, by Udacity.\\
\textsc{04/2017} & \href{https://brunoroque06.github.io/documents/certificates/MachineLearningCoursera.pdf}{Machine Learning}, by Stanford University on Coursera. % https://coursera.org/verify/SZ4MWSX9GNGN
}

\section{Achievements}
\tabularNoBar{
\textsc{03/2017} & Federated \href{http://ratings.fide.com/card.phtml?event=1958720}{Chess Player}.\\
\textsc{11/2016} & Open Water Diver, by PADI.\\
\textsc{01/2010} & Driving License B/B1.
}

\section{Languages}
\tabularNoBar{
\textsc{Portuguese:} & Native\\
\textsc{English:} & Proficient\\
\textsc{German:} & Intermediate (\href{https://brunoroque06.github.io/documents/certificates/GermanA2.pdf}{A2})
}
